Plot density of imputations

### 2020-02-22 3.Thesis/plot_imputation_densities.Rmd
update omdat laptop uitvalt

imputed_values[[1]]$bmi %>% mutate(case = row_number())
#map(imputed_values, function(x) map(vars, function(y) {print(x)}))#mutate(case = row_number())})) #%>%  tidyr::gather("imp", "value", 1:M) %>% .[order(.$case, .$imp),]}) 
test5 <- map(imputed_values, function(x) map(x, function(y) {as.data.frame(y) %>% mutate(case = row_number()) %>%  tidyr::gather("imp", "value", 1:M)}))  #%>% .[order(.$case, .$imp),]}) })) 
# case_mean <- imputed_values %>% group_by(case) %>% summarise(mu = mean(value), sigma = sd(value))

>>>>

imputed_values[[1]]$bmi %>% mutate(case = row_number())
#map(imputed_values, function(x) map(vars, function(y) {print(x)}))#mutate(case = row_number())})) #%>%  tidyr::gather("imp", "value", 1:M) %>% .[order(.$case, .$imp),]}) 
test5 <- map(imputed_values, function(.x) map(.x, function(.y) {as.data.frame(.y) %>% mutate(case = row_number()) %>%  tidyr::gather("imp", "value", 1:M)  %>% .[order(.$case),] %>% mutate(.x = .$value) }))#group_by(.$case) %>% summarise(mu = mean(.$value), sigma = sd(.$value))}) ) 
# case_mean <- imputed_values %>% group_by(case) %>% summarise(mu = mean(value), sigma = sd(value))
# test5[[1]]$bmi %>% group_by(case) %>% summarise(mu = mean(value), sigma = sd(value))  
test5[[1]] %>% map(vars, ~{.x %>% rename(bmi = value)})
